---
title: "BellBeat_Analysis"
author: "Vinay Tekkur"
date: "01/08/2021"
output: html_document
---

Following Questions to get insights from data
  1) Is Tracked Distance from user and sensor(tracker/device) is relative?
  2) How Daily activities effect the number of calories?
  3) How Daily activities effect to user weight?
  4) How Daily activities effect to user BMI?
  
  
#  Installing and Loading packages

```{r}
install.packages("tidyverse")
library(tidyverse)
```

# Load the DailyActivities Dataset
```{r}
dailyActivity_merged <- read_csv("dataset/dailyActivity_merged.csv")
```

## View the dataset
```{r}
View(dailyActivity_merged)
head(dailyActivity_merged)
```

## Get column names of dataset
```{r}
colnames(dailyActivity_merged)
```

# Relationship between TotalDistance and Tracker Distance
```{r}
ggplot(data=dailyActivity_merged) + 
  geom_point(mapping = aes(x = TotalDistance, y = TrackerDistance)) + 
  labs(title = "Total Distance by User Vs. Tracker Total Distance", subtitle = "Here we tracking distance travlled by user and distance collected by traker",
       x = "Total Distance", y = "Tracker Distance")
```
Conclusion: From Visualization it is clear that Distance from user and distance monitored by device or tracker are same except some noise


# Relationships between Total distance Vs Calories
```{r}
ggplot(data=dailyActivity_merged) + 
  geom_point(mapping = aes(x = TotalDistance, y = Calories)) + 
  labs(title = "Total Distance by User Vs. Calories", subtitle = "Here collecting data from Total distance travelled by user Vs Calories lost",
       x = "Total Distance")
```
Conclusion: If Activity increases Calories loss also increases


# Load the weightLogInfo_merged Dataset
```{r}
weightLogInfo_merged <- read_csv("dataset/weightLogInfo_merged.csv")
```

## View the dataset
```{r}
View(weightLogInfo_merged)
head(weightLogInfo_merged)
```

## Get column names of dataset
```{r}
colnames(weightLogInfo_merged)
```

# Get observations from both dataset
```{r}
nrow(dailyActivity_merged)
nrow(weightLogInfo_merged)
```

# Get Summary of DailyActivities dataset
Summary is calculated on Total Steps and Total Distance of user
```{r}
dailyActivity_merged %>%
  select(TotalSteps, TotalDistance) %>%
  summary()
```

# Get Summary of weightLogInfo_merged dataset
Summary is calculated on Total Steps and Total Distance of user
```{r}
weightLogInfo_merged %>%
  select(WeightKg, WeightPounds, BMI) %>%
  summary()
```


# Merging DailyActivities datset and weightLogInfo dataset
merging datasets based on "Id" which is common on both of the dataset
```{r}
combined_data <- merge(weightLogInfo_merged, dailyActivity_merged, by="Id")
```

## View the combined dataset
```{r}
View(combined_data)
head(combined_data)
```


# Relationships between Total distance Vs Weight of user in Kg
```{r}
ggplot(data=dailyActivity_merged) + 
  geom_point(mapping = aes(x = TotalDistance, y = Calories)) + 
  labs(title = "Total Distance by User Vs. Calories", subtitle = "Here collecting data from Total distance travelled by user Vs Calories lost",
       x = "Total Distance")
```
Conclusion: If Activity increases Weight of the user decreases


# Relationships between Total distance Vs Weight of user in pounds
```{r}
ggplot(data=combined_data) + 
  geom_smooth(mapping = aes(x = TotalDistance, y = WeightPounds)) + 
  labs(title = "Total Distance by User Vs. Weight in pounds", subtitle = "Here collecting data from Total distance travelled by user Vs Weight of user in pounds",
       x = "Total Distance",
       y = "Weight in pounds")
```
Conclusion: If Activity increases Weight of the user decreases


# Relationships between Total distance Vs BMI
```{r}
ggplot(data=combined_data) + 
  geom_smooth(mapping = aes(x = TotalDistance, y = BMI)) + 
  labs(title = "Total Distance by User Vs. BMI", subtitle = "Here collecting data from Total distance travelled by user Vs BMI",
       x = "Total Distance",
       y = "BMI")
```

Conclusion:
Q) Is Tracked Distance from user and sensor(tracker/device) is relative?
A) Based on analysis it id found that Distence tracked by device is valid 


Q) How Daily activities effect the number of calories?
A) If Activity increases Calories loss also increases


Q) How Daily activities effect to user weight?
A) If Activity increases Weight of the user decreases


Q) How Daily activities effect to user BMI?
A) If Activity increases BMI of the user decreases




